---
title: "Online Appendix: Supporting Information for _Introducing the International Crisis Behavior Event (ICBe) Dataset_"
authors:
  - name: Shannon Carcelli
    department: Department of Political Science
    affiliation: University of Maryland, College Park
    location: 
    email: 
  - name: Rex W. Douglass
    department: Department of Political Science
    affiliation: University of California, San Diego
    location: CA, USA
    email: 
  - name: J Andrés Gannon
    department: Department of Political Science
    affiliation: University of California, San Diego
    location: CA, USA
    email: 
  - name: Erik Gartzke
    department: Department of Political Science
    affiliation: University of California, San Diego
    location: CA, USA
    email: 
  - name: Jon Lindsay
    department: Munk School of Global Affairs and Public Policy and Department of Political Science
    affiliation: University of Toronto
    location: Toronto, ON, Canada
    email: jon.lindsay@utoronto.ca
  - name: Thomas Leo Scherer
    department: Department of Political Science
    affiliation: University of California, San Diego
    location: CA, USA
    email: tlscherer@ucsd.edu
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
bibliography: ICBintro.bib
output: 
  rticles::arxiv_article:
    keep_tex: true
header-includes:
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{titlesec}
  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
  - \usepackage{caption}
  - \usepackage[capposition=top]{floatrow}
  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
---

```{r echo=FALSE}
`%>%` <- magrittr::`%>%`
```

<!-- # (APPENDIX) Appendix {-}  -->
<!-- https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html -->
<!-- may require additional software -->

\begin{figure}[h]
\caption{Action Event Classification Tree\label{fig:event_action_tree}}
\centering{\includegraphics[width=17cm]{figures/event_action_tree}}
\end{figure}


\begin{figure}[h]
\caption{Graphical User Interface (GUI) for coding ICBED\label{fig:coding_gui}}
\centering{\includegraphics[width=17cm]{figures/gui_example}}
\end{figure}


\begin{figure}
\caption{Crisis Actors counts for ICB Project system-level data and for ICBe \label{fig:actors_by_crisis}}
\centering{\includegraphics[width=17cm]{figures/actors_by_crisis}}
\textit{Notes:} The number of perceived actors in each crisis as recorded by the ICB Project vs. the number of actors recorded in the ICBe dataset, with and without non-state actors.
\end{figure}


```{r echo=FALSE}
read.csv(paste0(here::here(), "/inst/extdata/","icb1v14.csv")) %>% dplyr::count(crismg) %>% 
  dplyr::mutate(crismg = dplyr::recode(crismg, `1` = "1: Negotiation", `2`="2: Adjudication", `3`= "3: Mediation", `4` = "4: Multiple excluding violence", `5` = "5: Non-military pressure", `6` = "6: Non-violent military", `7` = "7: Multiple including violence", `8` = "8: Violence")) %>%
  dplyr::rename(`Management Technique` = crismg) %>% 
  kableExtra::kbl(caption="Count of ICB Project Crisis-Level Management Technique \\label{tbl:ICBproject_crisis_management_technique}") %>% kableExtra::row_spec(0,bold=TRUE)
```


```{r echo=FALSE}
event_percent_diff_by_crismg <- readRDS(file=paste0(here::here(), "/data/event_percent_diff_by_crismg.rds"))

event_percent_diff_by_crismg_tableprep <- event_percent_diff_by_crismg %>% 
    dplyr::mutate(action_type = dplyr::recode(action_type, `thinkkind` = "Think", `sayintkind`="Speech", 
                                       `act_cooperative_clean` = "Cooperative", 
                                       `act_descalate_clean` = "De-escalatory ", 
                                       `act_escalate_clean` = "Escalatory", 
                                       `act_uncooperative_clean` = "Uncooperative", 
                                       `interact_decreasecoop_clean` = "Uncooperative", 
                                       `interact_increasecoop_clean` = "Cooperative", 
                                       `interact_descalate_clean` = "De-escalatory ", 
                                       `interact_escalate_clean` = "Escalatory")) %>% 
  dplyr::arrange(desc(All)) %>% 
  dplyr::slice_head(n=20) 
  
event_percent_diff_by_crismg_tableprep <- dplyr::bind_cols(event_percent_diff_by_crismg_tableprep[1:3],
  lapply(event_percent_diff_by_crismg_tableprep[4:11], function(x) {
  x.c <- paste0(ifelse(x > 0, "+", ""), round(x, digits = 2))}))
```


```{r echo=FALSE}
event_percent_diff_by_crismg_tableprep %>%  dplyr::mutate(action = dplyr::recode(action, `invasion/occupation` = "invasion / occupation")) %>% 
  dplyr::rename(`All Crises` = "All", `CMT 1: Negotiation` = "1: Negotiation", `CMT 2: Adjud`="2: Adjudication", `CMT 3: Medi`= "3: Mediation", `CMT 4: Multi no violence` = "4: Multiple excluding violence", `CMT 5: Non-mil pressure` = "5: Non-military pressure", `CMT 6: Non-violent mil` = "6: Non-violent military", `CMT 7: Multi with violence` = "7: Multiple including violence", `CMT 8: Violence` = "8: Violence") %>% 
  dplyr::select(-`CMT 2: Adjud`, -`CMT 3: Medi`, -`CMT 5: Non-mil pressure`) %>%
  kableExtra::kbl(caption="Average Percentage of Event Types in a Crisis by Management Technique (CMT) \\label{tbl:crismg_count_mean_table}")  %>%
  # kableExtra::kable_styling() %>% 
  kableExtra::column_spec(2, latex_column_spec = "p{1.8cm}") %>%
  kableExtra::column_spec(4, latex_column_spec = "p{1.2cm}") %>%
  #kableExtra::column_spec(5, latex_column_spec = "p{.8cm}") %>%
  #kableExtra::column_spec(6, latex_column_spec = "p{.8cm}") %>%
  kableExtra::column_spec(5, latex_column_spec = "p{1.4cm}") %>%
  #kableExtra::column_spec(8, latex_column_spec = "p{1cm}") %>%
  kableExtra::column_spec(6, latex_column_spec = "p{1.4cm}") %>%
  kableExtra::column_spec(7, latex_column_spec = "p{1.4cm}") %>%
  kableExtra::column_spec(8, latex_column_spec = "p{1.4cm}")
  # kableExtra::column_spec(8, width = "1.4cm") %>% 
  # kableExtra::collapse_rows()
```


\begin{figure}
\caption{Crisis event counts from Phoenix and ICB for crises with and without USA\label{fig:phoenix_event_counts_usa}}
\centering{\includegraphics[width=17cm]{figures/phoenix_event_counts_usa}}
\end{figure}


```{r echo=FALSE, message=FALSE}
readRDS(file=paste0(here::here(), "/data/liberia_sierraleone_phoenix.Rds"))%>% 
  kableExtra::kbl(caption="Phoenix Events for Liberia / Sierra Leone (Crisis 395) \\label{tbl:liberia_sierraleone_phoenix}") %>%  
  kableExtra::column_spec(4, latex_column_spec = "p{1cm}") %>%
  kableExtra::column_spec(5, latex_column_spec = "p{7cm}")
  # kableExtra::column_spec(2, width = "1cm")
```

```{r echo=FALSE, message=FALSE}
readRDS(file=paste0(here::here(), "/data/liberia_sierraleone_extended.Rds")) %>% 
  kableExtra::kbl(caption="Extended Phoenix Events for Liberia / Sierra Leone (Crisis 395) \\label{tbl:liberia_sierraleone_phoenix_extended}") %>%  
  kableExtra::column_spec(4, latex_column_spec = "p{1cm}") %>%
  kableExtra::column_spec(5, latex_column_spec = "p{7cm}")
  # kableExtra::column_spec(2, width = "1cm")
```


```{r echo=FALSE, message=FALSE}
drc_icb <- readRDS(file=paste0(here::here(),"/data/drc_icb.Rds"))

drc_required_phoenix <- readRDS(file=paste0(here::here(), "/data/drc_required_phoenix.Rds")) 

drc_required_phoenix_table <- readRDS(file=paste0(here::here(), "/data/drc_required_phoenix_table.Rds")) 

```

```{r echo=FALSE, message=FALSE}
data.frame(lapply(drc_icb, function(x) {gsub("democratic_republic_of_the_congo", "DRC", x)})) %>% 
  dplyr::select(-sentence_number_int_aligned) %>% 
  dplyr::slice(16:41) %>%
  kableExtra::kbl(caption="ICBe Dataset for DRC Civil War (Crisis 426) around August 1998 \\label{tbl:drc_icb}") %>%
  kableExtra::column_spec(1, latex_column_spec = "p{1.8cm}") %>%
  kableExtra::column_spec(2, latex_column_spec = "p{3.5cm}") %>%
  kableExtra::column_spec(3, latex_column_spec = "p{2.5cm}") %>% 
  kableExtra::column_spec(5, latex_column_spec = "p{3.5cm}")
```


```{r echo=FALSE, message=FALSE}
drc_required_phoenix_table %>% 
  dplyr::select(`Story Date`, Source, Target, `Event Code`, Event, Corpus) %>% 
  dplyr::slice_head(n=20) %>%
  kableExtra::kbl(caption="First 20 Phoenix Events (DRC-required) for DRC Civil War (Crisis 426) \\label{tbl:drc_civil_war_start_phoenix}") %>%  
  kableExtra::column_spec(4, latex_column_spec = "p{1cm}") %>%
  kableExtra::column_spec(5, latex_column_spec = "p{7cm}")
  # kableExtra::column_spec(2, width = "1cm")
```


```{r echo=FALSE, message=FALSE}
drc_required_phoenix %>% dplyr::filter(year == "2001" & month == "01") %>% dplyr::count(EventDescription, sort=TRUE) %>%
  kableExtra::kbl(caption="Phoenix Events (DRC-required) for January 2001 DRC Civil War (Crisis 426) \\label{tbl:drc_civil_war_jan2001_phoenix}")
  # kableExtra::column_spec(2, width = "1cm")
```

